Polyester RNA-seq simulation study

### 2018-07-18 datasets/RNA-Seq/polyester-simulation.Rmd
Standardize number of DE genes

  geneExp <- tbl_df(data.frame(geneName=rownames(counts),
                               pval=res_alt$pvalue, SE=res_alt$lfcSE, 
                               ind_covariate = ifelse(uninformativeCovariate, 
                                                      uninf_covar,
                                                      res_alt$baseMean), 
                               effect_size=res_alt$log2FoldChange, 
                               test_statistic=res_alt$stat, qvalue=truth, 
                               pzero = rowSums(counts(dds_alt)==0)/
                                 ncol(counts(dds_alt))  ))

@@

Here we'll repeat the above, but for a DE comparison 5 versus 5 samples
and 1500 DE genes are added. This will be done for 100 simulations.

@@

```{r, results='hide', message=FALSE}
sampleSize <- 5
nDE <- 1500
rseed <- 198

@@

Here we'll repeat the above, but for a DE comparison 10 versus 10 samples
and 1500 DE genes are added. This will be done for 100 simulations.

@@

```{r, results='hide', message=FALSE}
sampleSize <- 10
nDE <- 1500
rseed <- 961

>>>>

  geneExp <- tbl_df(data.frame(geneName=rownames(counts),
                               pval=res_alt$pvalue, SE=res_alt$lfcSE, 
                               ind_covariate = res_alt$baseMean, 
                               effect_size=res_alt$log2FoldChange, 
                               test_statistic=res_alt$stat, qvalue=truth, 
                               pzero = rowSums(counts(dds_alt)==0)/
                                 ncol(counts(dds_alt))  ))

  if (uninformativeCovariate)
    geneExp <- mutate(geneExp, ind_covariate = uninf_covar)

@@

Here we'll repeat the above, but for a DE comparison 5 versus 5 samples
and 2000 DE genes are added. This will be done for 100 simulations.

@@

```{r, results='hide', message=FALSE}
sampleSize <- 5
nDE <- 2000
rseed <- 198

@@

Here we'll repeat the above, but for a DE comparison 10 versus 10 samples
and 2000 DE genes are added. This will be done for 100 simulations.

@@

```{r, results='hide', message=FALSE}
sampleSize <- 10
nDE <- 2000
rseed <- 961
